---
title: "Project Report"
author: "Gianna DeLorenzo & Sara Almansoori"
format: pdf
editor: visual
bibliography: references.bib  
csl: apa7.csl  
---

# Introduction

Education is the foundation of many countries worldwide. It is a fundamental right to have access to these tools. 
Over the past decade, global and regional efforts have been focusing on improving individuals' access to education, 
more specifically secondary education, addressing socio-economic disparities and integrating online learning tools; 
however, issues still arise within these efforts in providing equal education and access for all individuals. It is a 
social issue that affects everyone, whether indirectly or directly, and presents unequal treatment towards individuals' 
with less access to the same tools based on their regions and/or class levels. 

In this report, we will be investigating the following research questions: 
1. What are the global and regional trends in secondary schools enrollment rates over the past 10 years? 

This research question explores patterns globally and regionally in terms of access to education. It focuses on the 
enrollment rates of adolescents of secondary school age. 

2. How do socio-economic factors correlate with individuals' access to quality education and development? 

This research question explores the patterns associated with socio-economic factors, and how they are connected with 
access to quality education and development. It goes into depth about which socio-economic factors impact this access 
the most and 

3. How does individuals' access to online learning tools differentiate according to the region and class levels, and what impact does this 
have on learning? 

We will first present the provenance of the data. Then, how it aligns with the FAIR and/or CARE principles. Then we will present 
the methodology of the data and the analysis attributes. After, we will explore the data visualizations and the results. Finally, 
we will close up the report with a discussion of our findings.

## Provenance

The dataset used for this analysis, the 'Learning and Skills' dataset from UNICEF, explores the global educational indicators ranging 
from 2016 to 2023. The indicators integrated include the percentage of children of lower secondary school age attending lower secondary 
school or higher, the percentage of children of upper secondary school age attending upper secondary school or higher

We obtained the data from UNICEF which is the United Nations Children's Fund. It is a UN agency that is responsible for providing 
assistance to children worldwide pertaining humanitarian and developmental factors.

## FAIR and/or CARE Principles

# Methodology

## Analysis Attributes

# Data Exploration

## Visualization 1

```{r}
#| label: load-packages
#| include: false
#| echo: false

#Load necessary libraries
library(dplyr)
library(kableExtra)

#Import UNICEF csv file
unicef_data <- read.csv("UNICEF Dataset.csv")

# Load Column Names
colnames(unicef_data)

#Summary Statistics
unicef_summary_table <- unicef_data %>%
  group_by(REF_AREA.Geographic.area) %>%
  summarise(
    mean_value = mean(OBS_VALUE.Observation.Value, na.rm = TRUE),
    minimum_value = min(OBS_VALUE.Observation.Value, na.rm = TRUE),
    median_value = median(OBS_VALUE.Observation.Value, na.rm = TRUE),
    maximum_value = max(OBS_VALUE.Observation.Value, na.rm = TRUE),
    count = n()
  )

#Format the Summary Statistics in a Table using Kable Styling
unicef_summary_table %>%
  kable(format = 'html',
        caption = 'Global Dataflow UNICEF',
        col.names = c('Geographic Area', 'Mean', 'Minimum', 
                      'Median', 'Maximum', 'Count')
        ) %>%
  kable_styling(full_width = FALSE)

```

## Visualization 2

```{r}

#Load necessary libraries
library(ggplot2)

#Import UNICEF csv file
unicef_data <- read.csv("UNICEF Dataset.csv")

#Create the Visualization
unicef_plot <- ggplot(unicef_data,
                      aes(x = OBS_VALUE.Observation.Value, 
                          y = as.factor(TIME_PERIOD.Time.period),
                          color = REF_AREA.Geographic.area)) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Unicef Time Period vs. Observation Value by Geographic Area",
    x = "Observation Value",
    y = "Time Period",
    color = "Geographic Area"
  ) +
  theme_minimal()

unicef_plot

```

## Visualization 3

# Results

# Conclusion 

# References

# Code Appendix

```{r codeAppend, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}

```

