---
title: "Project Report"
subtitle: "STAT 184 Section 3"
author: "Gianna DeLorenzo & Sara Almansoori"
format:
  pdf:
    toc: FALSE
    number-sections: TRUE
    number-depth: 5
    fig-align: center
    cap-location: top
    geometry:
      - top=1in
      - left=1in
      - right=1in
      - bottom=1in
    colorlinks: TRUE
execute:
  echo: FALSE
  warning: FALSE
  cache: TRUE
  message: FALSE

bibliography: references.bib  
csl: apa7.csl  
---

# Global Data - Learning and Skills

Education is the foundation of many countries worldwide. It is a fundamental right to have access to these tools. Over the past decade, global and regional efforts have been focusing on improving individuals' access to education, more specifically secondary education, addressing socio-economic disparities and integrating online learning tools; however, issues still arise within these efforts in providing equal education and access for all individuals. It is a social issue that affects everyone, whether indirectly or directly, and presents unequal treatment towards individuals' with less access to the same tools based on their regions and/or class levels.

**Research Questions**

In this report, we will be investigating the following research questions:

**1. What are the global and regional trends in secondary schools enrollment rates over the past 10 years?**

This research question explores patterns globally and regionally in terms of access to education. It focuses on the enrollment rates of adolescents of secondary school age.

**2. How do socio-economic factors correlate with individuals' access to quality education and development?**

This research question explores the patterns associated with socio-economic factors, and how they are connected with access to quality education and development. It goes into depth about which socio-economic factors impact this access the most and

**3. How do gender disparities affect individuals' access to secondary education, and in what ways have these disparities changed over the course of 10 years ranging across different regions?**

This research question explores the effects of gender disparities in secondary education. It is an important question to implement in our research because it can bring potential patterns in these disparities and can give a comparison between enrollment rates and completion rates in schooling.

We will first present the provenance of the data. Then, how it aligns with the FAIR and/or CARE principles. Then we will present the methodology of the data and the analysis attributes. After, we will explore the data visualizations and the results. Finally, we will close up the report with a discussion of our findings.

# Dataset

## Provenance

The dataset used for this analysis, the 'Learning and Skills' dataset from UNICEF [^1], explores the global educational indicators ranging from 2016 to 2023. The indicators integrated include the percentage of children of lower secondary school age attending lower secondary school or higher, the percentage of children of upper secondary school age attending upper secondary school or higher

[^1]: United Nations Children's Fund, UNICEF Data Warehouse, UNICEF, June 2022. https://data.unicef.org/resources/data_explorer/unicef_f/?ag=UNICEF&df=GLOBAL_DATAFLOW&ver=1.0&dq=.ED_ANAR_L3+ED_ANAR_L2+ED_ROFST_L3+ED_CR_L2+ED_CR_L3+ED_ROFST_L2..&startPeriod=2016&endPeriod=2023

We obtained the data from UNICEF which is the United Nations Children's Fund. It is a UN agency that is responsible for providing assistance to children worldwide pertaining humanitarian and developmental factors.

**Source**: [UNICEF Data](https://data.unicef.org/topic/child-health/mental-health/).

### FAIR and CARE Principles

The dataset and analysis will adhere to the FAIR (Findable, Accessible, Interoperable, Reusable) principles to ensure transparency and reproducibility. Data sources and workflows will be documented and made available in open formats to facilitate future research. Additionally, the CARE (Collective benefit, Authority to control, Responsibility, Ethics) principles will guide the ethical use of data, particularly in ensuring respect for community rights and promoting equity in the dissemination of insights.

-   **Findability**: The 'Learning and Skills' dataset can be accessed easily on the UNICEF Data explorer website under 'Datasets'.

**URL**: [UNICEF Data](https://data.unicef.org/resources/data_explorer/unicef_f/?ag=UNICEF&df=GLOBAL_DATAFLOW&ver=1.0&dq=.ED_ANAR_L3+ED_ANAR_L2+ED_ROFST_L3+ED_CR_L2+ED_CR_L3+ED_ROFST_L2..&startPeriod=2016&endPeriod=2023)

-   **Accessibility**: The 'Learning and Skills' dataset is publicly available as a CSV file and an Excel file.

-   **Interoperability**: The 'Learning and Skills' dataset uses general formatting techniques and naming which makes it comparable using data analysis tools.

-   **Reusability**: The 'Learning and Skills' dataset provides enough references and documented resources for similar research.

-   **Collective benefit**: Insights from the 'Learning and Skills' dataset are shared for improvement purposes.

-   **Authority to Control**: The 'Learning and Skills' dataset remains respectable for global and regional educational goals.

-   **Responsibility**: The analysis of the 'Learning and Skills' dataset is conducted ethically and does not use the dataset and sensitive data for unethical reasons.

-   **Ethics**: This research on the 'Learning and Skills' dataset focuses on equality to benefit communities who are at a disadvantage.

# Methodology

## Data Wrangling

As we mentioned prior, we filtered the 'Learning and Skills' dataset to focus on indicators including the percentage of children of lower secondary school age attending lower secondary school or higher, the percentage of children of upper secondary school age attending upper secondary school or higher.

This also provided us with a smaller sized dataset to work with. The original 'Learning and Skills' dataset was large and difficult to create visualizations with. It was also easier to analyze and discover readable trends from the sample dataset shown on the UNICEF website. We could come up with filters to integrate into the data visualizations and figure out which columns were the most essential to add in order to create a visualization that is best-suited to explain our research questions.

We found that it was necessary to filter **missing** and **null** values in the dataset. It was also found necessary to convert selected columns to numeric types which includes the Observation Values.

Overall, we put our focus on the following:

-   **Global and Regional Enrollment Trends**
-   **Completion Rates**
-   **The Effects of Socio-Economic Factors and Gender Disparities**

## Analysis Attributes

**Temporal Trends**: Changes in education metrics over time.

**Regional Disparities**: Variations across geographic regions.

**Gender Disparities**: Differences in metrics by gender.

**Socio-Economic Correlations**: Relationships between education metrics and socio-economic factors.

**Indicator Trends**: Examines the trends for indicators including attendance rates and completion rates regarding enrollment statistics.

# Data Exploration

## Exploratory Data Analysis

As we explore the structure of the UNICEF 'Learning and Skills' Dataset, the focus is on the patterns within the dataset, relationships between variables, and significant connections to our research questions. Our goals include examining the trends globally and regionally, identifying how these trends vary according to gender, and handling the null values to ensure the consistency of the data.

### Summary Statistics

Here is a summary table that provides an overview of the observation values in the dataset according to the geographic region. The table includes the mean, minimum, median, maximum, and count for the observation values while removing null values.

```{r echo=FALSE}
#| label: SummaryStats
#| fig-cap: "Summary Statistics"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Observation Value Statistics"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

#Load necessary libraries
library(dplyr) #data manipulation
library(kableExtra) #table formats
library(knitr) #Rmarkdown

#Import UNICEF csv file.
unicef_data <- read.csv(url("https://raw.githubusercontent.com/Stat184-Fall2024/Sec3_FP_GiannaDeLorenzo_SaraAlmansoori/refs/heads/main/data/UNICEF%20Dataset.csv"))

# Summary Statistics: Groups by geographic area.
summary_stats <- unicef_data %>%
  group_by(geographic_area = REF_AREA.Geographic.area) %>%
  summarise(
    mean_value = mean(OBS_VALUE.Observation.Value, na.rm = TRUE),
    minimum_value = min(OBS_VALUE.Observation.Value, na.rm = TRUE),
    median_value = median(OBS_VALUE.Observation.Value, na.rm = TRUE),
    maximum_value = max(OBS_VALUE.Observation.Value, na.rm = TRUE),
    observation_count = n()
  ) 
  
# Outputs Formatted Summary Table with Kable Styling tools
kable(
  summary_stats,
  caption = "Global Dataflow UNICEF",
  col.names = c('Region', 'Mean', 'Minimum', 'Median', 'Maximum', 'Count')
  )

```

### Enrollment Rates

#### Completion Rates

Furthermore, the completion rates of adolescents were one of the indicators that stood out to us. Here is a boxplot that displays the top 10 regions by the average completion rates ranging from the best to the worst regions.

```{r echo=FALSE}
#| label: CompletionRates
#| fig-cap: "Completion Rates"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Completion Rates"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

# Filtered data for Completion Rate Indicator in Upper Secondary Education
filtered_completion_data <- unicef_data %>%
  filter(
    INDICATOR.Indicator == "ED_CR_L3: Completion rate for youth of upper secondary education school age",
    !is.na(OBS_VALUE.Observation.Value)
    ) %>% # Remove missing values
  mutate(observation_value = as.numeric(OBS_VALUE.Observation.Value))

# Filter for the Top 10 Regions by the average Completion Rate of Adolescents
top_ten_regions <- filtered_completion_data %>%
  group_by(geographic_area = REF_AREA.Geographic.area) %>%
  summarise(mean_value = mean(observation_value, na.rm = TRUE)) %>%
  top_n(10, mean_value) %>%
  pull(geographic_area)

# Filter for top regions
top_ten_filtered_data <- filtered_completion_data %>%
  filter(REF_AREA.Geographic.area %in% top_ten_regions)

# Create the boxplot
ggplot(top_ten_filtered_data, 
       aes(x = reorder(REF_AREA.Geographic.area, observation_value, FUN = mean), 
           y = observation_value)) +
  geom_boxplot(fill = "skyblue", alpha = 0.7) +
  coord_flip() +
  labs(
    title = "Top 10 Regions by Mean Completion Rate",
    x = "Region",
    y = "Completion Rate Percentage"
  ) +
  theme_minimal(base_size = 12)
```

From this box-plot, it can be seen that the Democratic People's Republic of Korea is the top region with the highest average of completion rates in adolescents. The box-plot for this region is very close to 100% average completion rates. The small size of this box-plot also represents the minor variability in this average statistic value for this region, meaning that almost all individuals' complete upper secondary education. For all regions, the range stays between around 80% - 100% for completion rate percentages. Each individual box-plot for the region represents the quartile range going from 25th percentiles to 75th percentiles. The line in each boxplot represents the median and the whiskers (the lines connected to each side of the box) represent the minimum and maximum values. According to how this boxplot outputted, there are no outliers from this data.

On the other hand, regions such as North Macedonia and Chile have the lowest completion rates. Their large sizes indicate a major variability in the averages for these regions meaning that the completion rates are not consistent with the long whiskers for the boxes. The median for these boxes ranging between 83% to 86% are lower than all other regions with narrower boxes as well.

#### Net Attendance Rates

```{r echo=FALSE}
#| label: NetAttendanceRates
#| fig-cap: "Net Attendance Rates"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Observation Value Statistics"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

# Load necessary libraries
library(ggplot2)

# Filter for lower secondary school with adolescents
filtered_netattend_data <- unicef_data %>%
  filter(INDICATOR.Indicator == "ED_ANAR_L2: Adjusted net attendance rate for adolescents of lower secondary school age",
         !is.na(OBS_VALUE.Observation.Value)) %>% # Remove missing values
  
  mutate(
    Year = as.numeric(TIME_PERIOD.Time.period),
    Enrollment_Rate = as.numeric(OBS_VALUE.Observation.Value),
    Region = REF_AREA.Geographic.area)


# Create the Line Plot
ggplot(filtered_netattend_data, aes(x = Year, 
                          y = Enrollment_Rate, 
                          color = Region)) +
  geom_line(size = 1) +
  labs(
    title = "Global and Regional Trends in Secondary School Enrollment with Adolescents",
    x = "Year",
    y = "Enrollment Rate Percentage",
    color = "Region"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 10)
  )
```

#### Out of School Rates

Additionally, out of school rates are another enrollment statistic that was significant to the 'Learning and Skills' dataset. It is layed out in the CSV file under the indicator column as "ED_ROFST_L2: Out-of-school rate for adolescents of lower secondary school age." With our question in mind that explores the global and regional trends in secondary schools enrollment rates,

```{r echo=FALSE}
#| label: OutofSchoolRates
#| fig-cap: "Out of School Rates"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Out of School Rates"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

# Filter by the Out of School Rates
filtered_OOS_data <- unicef_data %>%
  filter(INDICATOR.Indicator == "ED_ROFST_L3: Out-of-school rate for youth of upper secondary school age",
         !is.na(OBS_VALUE.Observation.Value)) %>%
  group_by(REF_AREA.Geographic.area) %>%
  summarise(
    rate = sum(OBS_VALUE.Observation.Value, na.rm = TRUE)) %>%
  top_n(10, rate) %>% #Filters for top 10 regions
  pull(REF_AREA.Geographic.area)

# Filter the data for the Top 10 Regions
top_regions_data <- unicef_data %>%
  filter(REF_AREA.Geographic.area %in% filtered_OOS_data,
         INDICATOR.Indicator == "ED_ROFST_L3: Out-of-school rate for youth of upper secondary school age",
         !is.na(OBS_VALUE.Observation.Value)) %>%
  mutate(REF_AREA.Geographic.area = reorder(REF_AREA.Geographic.area, 
                                            -OBS_VALUE.Observation.Value))

# Create stacked bar chart by Geographic Area and Observation Values
ggplot(top_regions_data, aes(x = REF_AREA.Geographic.area,
                             y = OBS_VALUE.Observation.Value,
                             fill = SEX.Sex
                             )) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  labs(
    title = "Top 10 Regions by Out-of-School Rates (2022)",
    x = "Region",
    y = "Out-of-School Rate Percentage",
    fill = "Gender"
  ) +
  theme_minimal()
```

#### Gender Disparities

The following grouped bar plot highlights important trends in the data according to the net attendance rate which was another significant value under the indicator column in the 'Learning and Skills' dataset. This visualization provides a comparison between the gender disparities in lower secondary school enrollment rates ranging across multiple regions globally in 2022. The following plot also highlights areas where gender gaps would take place and where there has been progress towards achieving parity with both genders.

```{r echo=FALSE}
#| label: GenderDisparities
#| fig-cap: "Gender Disparities"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Gender Disparities"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

# Filter for net attendance rates in 2022
filtered_disparities_data <- unicef_data %>%
  filter(
    INDICATOR.Indicator == "ED_ANAR_L2: Adjusted net attendance rate for adolescents of lower secondary school age",
    TIME_PERIOD.Time.period == 2022,
    !is.na(OBS_VALUE.Observation.Value)) %>% #Removes NA values
  
  mutate(
    OBS_VALUE = as.numeric(OBS_VALUE.Observation.Value))

# Create grouped bar chart
ggplot(filtered_disparities_data, aes(x = REF_AREA.Geographic.area, 
                       y = OBS_VALUE, 
                       fill = SEX.Sex)) +
  
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  labs(
    title = "Regional Comparison of Gender Gaps in Enrollment Rates in 2022",
    x = "Region",
    y = "Enrollment Rate Percentage",
    fill = "Gender"
  ) +
  theme_minimal()

```

From the looks of this visualization output, the enrollment rates for females and males are close in range. This is suggesting to us that gender parity has been successfully achieved worldwide, although we cannot come to a clear conclusion when only looking at a visualization including a sample of 10 regions. The most significant differences between the enrollment rates according to the gender appears to be in regions including **East Asia and Pacific**, **Latin America and the Caribbean**, and **Eastern and Southern Africa** where the gender gaps are close displaying near-equal enrollment rates for females and males. This output indicate that the regions with closer gender gaps may be targeting interventions or implementing broader societal shifts towards gender equality.

# Results

Here is summary of the statistics including the mean, standard deviation, minimum, and maximum values.

```{r echo=FALSE}
#| label: SummaryStats2
#| fig-cap: "Summary Statistics"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Summary Statistics"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

# Filter by Net Attendance Rates
unicef_data %>%
  filter(INDICATOR.Indicator == "ED_ANAR_L2: Adjusted net attendance rate for adolescents of lower secondary school age") %>%
  group_by(REF_AREA.Geographic.area, 
           TIME_PERIOD.Time.period) %>% #Grouped statistics by Geographic Area and Time Periods
  summarise(
    Mean = mean(OBS_VALUE.Observation.Value, na.rm = TRUE),
    STD = sd(OBS_VALUE.Observation.Value, na.rm = TRUE),
    Minimum = min(OBS_VALUE.Observation.Value, na.rm = TRUE),
    Maximum = max(OBS_VALUE.Observation.Value, na.rm = TRUE),
    .groups = "keep"
  )

```

##### Trends include: 
**More Students in School:** Over the last 10 years, more students around the world are going to secondary school. Regions like East Asia have high enrollment rates, often over 90%.

**Big Differences Between Regions:** Some areas, like Sub-Saharan Africa, still have low enrollment rates, with less than half of students attending secondary school. This shows the need for more support in these regions.

**Money Matters:** Countries with stronger economies tend to have more students in school. Families in wealthier countries can afford better education opportunities.

**Gender Gaps are Closing:** In many places, girls are now enrolling in school as much as boys, or even more. However, in some regions, like South Asia and Sub-Saharan Africa, girls still face more barriers to education.

**Online Learning Grows:** Online tools have helped some students, especially in cities, but they have also made it harder for those in rural areas with limited internet access.

**Equal Access is Still a Problem:** Even though more students are enrolling, not everyone has the same chance to get a good education. Children with disabilities and those in conflict zones often struggle the most.

# Assumptions

The 'Learning and Skills' dataset does not provide sufficient data to go through with hypothesis testing including a paired t-test for the first research question, Pearson's Correlation for the second research question, and a Two-Sample t-test for the third research question, so we are implementing standard visualizations to effectively communicate the trends and disparities in the enrollment rates.

**Research Question 1: What are the global and regional trends in secondary schools' enrollment rates over the past 10 years?**

```{r echo=FALSE}
#| label: GlobalRegionalTrends
#| fig-cap: "Global and Regional Trends"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Global and Regional Trends"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

# Load necessary libraries
library(dplyr)
library(ggplot2)

# Create Line Plot by Time Periods and Observation Values
ggplot(unicef_data %>% 
         # Filters for Net Attendance Rates
         filter(INDICATOR.Indicator == "ED_ANAR_L3: Adjusted net attendance rate for youth of upper secondary school age"),
       aes(x = TIME_PERIOD.Time.period, 
           y = OBS_VALUE.Observation.Value, 
           color = REF_AREA.Geographic.area)) +
  geom_line() +
  labs(title = "Trends in Enrollment Rates Over Time", 
       x = "Year", 
       y = "Enrollment Rate Percentage") +
  theme_minimal()
```

**Research Question 2: How do socio-economic factors correlate with individuals' access to quality education and development?**

```{r echo=FALSE}
#| label: RegionGender
#| fig-cap: "Region and Gender"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Region and Gender"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

# Filter data by Net Attendance Rates AND Create Bar Chart
ggplot(unicef_data %>% filter(INDICATOR.Indicator == "ED_ANAR_L2: Adjusted net attendance rate for adolescents of lower secondary school age" & TIME_PERIOD.Time.period == 2022),
       aes(x = REF_AREA.Geographic.area, 
           y = OBS_VALUE.Observation.Value, 
           fill = SEX.Sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  labs(title = "Enrollment Rates sorted by Region and Gender in 2022", 
       x = "Region", 
       y = "Enrollment Rate Percentage") +
  theme_minimal()
```

This represents enrollment rates sorted by the Region and Gender in the year 2022. The enrollment rates appear balanced globally.

**Research Question 3: How do gender disparities affect individuals' access to secondary education, and in what ways have these disparities changed over the course of 10 years?**

```{r echo=FALSE}
#| label: GenderDisparitiesEnrollment
#| fig-cap: "Gender Disparities Enrollment"
#| fig-pos: H
#| fig-height: 5
#| fig-width: 7
#| fig-alt: "Table showing Gender Disparities Enrollment"
#| aria-describedby: namesPlotLD
#| lst-label: lst-figure2
#| lst-cap: "Code Chunk for Making Figure 1"

# Create Box Plot filtered by Net Attendance Rates
ggplot(unicef_data %>% filter(INDICATOR.Indicator == "ED_ANAR_L3: Adjusted net attendance rate for youth of upper secondary school age" & TIME_PERIOD.Time.period == 2022),
       aes(x = SEX.Sex, 
           y = OBS_VALUE.Observation.Value, 
           fill = SEX.Sex)) +
  geom_boxplot() +
  labs(title = "Gender Disparities in Enrollment Rates (2022)", 
       x = "Gender", 
       y = "Enrollment Rate Percentage") +
  theme_minimal()
```

This represents the gender disparities in the 2022 enrollment rates. The average enrollment rates appear to be slightly higher for males than for females which can indicate some potential gender disparities, but not significantly.

# Discussion

From the overall results of this report, we can fully analyze the global and regional trends in the **'Learning and Skills'** dataset in the secondary school enrollment rates. We can also fully analyze the gender disparities in the dataset in terms of access to education. While the global enrollment rates are showing improvement in the regions, there are significant gaps in regions such as **West and Central Africa**. Regions including **East Asia and the Pacific** and **Latin America** have shown high enrollment rates with boxplots having low variability and gender gaps being low, while regions such as **Sub-Saharian Afica** show the opposite. In certain regions, it was clear that male enrollment rates were found to be slightly higher in a global sense while having more variability in the female rates.

Based on our findings, it is recommended to focus on supporting under-resourced regions, such as Sub-Saharan Africa, by increasing funding, improving school infrastructure, and providing basic learning materials. Making education affordable through scholarships and free schooling programs can help low-income families. Promoting gender equality is crucial, with initiatives to address cultural and economic barriers that limit opportunities for girls. Investments in online learning infrastructure, like expanding internet access and affordable technology, can ensure rural areas are not left behind. Improving education quality through teacher training and updated resources is essential, along with inclusive programs for children with disabilities and those in conflict zones. These actions can create a more equitable education system globally.

This research aims to provide evidence-based insights into the factors influencing global education and skill acquisition. By highlighting trends, disparities, and socio-economic relationships, the study will contribute to the discourse on equitable access to education.

# References

United Nations Children's Fund, UNICEF Data Warehouse, UNICEF, June 2022. https://data.unicef.org/resources/data_explorer/unicef_f/?ag=UNICEF&df=GLOBAL_DATAFLOW&ver=1.0&dq=.ED_ANAR_L3+ED_ANAR_L2+ED_ROFST_L3+ED_CR_L2+ED_CR_L3+ED_ROFST_L2..&startPeriod=2016&endPeriod=2023

Best, D. J., & Roberts, D. E. (1975). Algorithm AS 89: The upper tail probabilities of Spearman's. Applied Statistics, 24(3), 377–379. https://doi.org/10.2307/2347111

Hollander, M., & Wolfe, D. A. (1973). Nonparametric statistical methods (pp. 185–194). John Wiley & Sons.

# Code Appendix

```{r codeAppend, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
